Technical Report

### 2024-04-30 Reports/tech_report1.tex
update report

>>>>

When do the test of layer 5, we read the accurate bounds information (open all nodes) of layer 3: \verb*|Diamond_record_6_100image59_dictionary_with_end_layer3_2024_04_23_17_02_11.b|

\subsection*{Method for part1}

\subsection*{Methods for part2}

The basic formula is as following:

\begin{align*}
	comp(b,b') &= \sum_{a}\sum_{c,c'\in C} u(a)\min(|W_{abcd}|,|W_{ab'c'd}|)\\
	comp(b) &= \sum_{b'\in B} comp(b,b')
\end{align*} Here, $d$ is the fixed target node. $B$ and $C$ are two specific sets. They can be all nodes in that layer, or more complex.
